Pteropod biomarker analysis

### 2018-03-02 index.Rmd
heatplot for model predictions

renderPlot({
  plot(effect(trm(), md(), xlevels = levs2()), multiline = T)
}, height = 300, width = 600)
```

>>>>

renderPlot({
  plot(effect(trm(), md(), xlevels = levs2()), multiline = T)
}, height = 300, width = 600)

renderPlot({

  x <- md()$model %>% 
    .[, -1] %>% 
    data.frame %>% 
    as.list %>% 
    map(range) %>%
    map(function(x) seq(x[1], x[2], length = 100))

  nms <- names(x) 
  x <- crossing(x[[1]], x[[2]])
  names(x) <- nms

  prd_vl <- predict(md(), newdata = x) %>% 
    data.frame(., x)
  names(prd_vl)[1] <- all.vars(formula(md()))[1]

  p <- ggplot(prd_vl, aes_string(y = names(prd_vl)[2], x = names(prd_vl)[3], fill = names(prd_vl)[1])) + 
    geom_tile(colour = 'black') + 
    pbase +
    scale_y_discrete(expand = c(0, 0)) + 
    scale_x_discrete(expand = c(0, 0)) +
    scale_fill_distiller(palette = 'Spectral') +
    guides(fill = guide_colourbar(barheight = 0.5, barwidth = 5, label.theme = element_text(size = 12, angle = 0)))
  p
}, height = 700, width = 700)
```
